### 2021-04-22 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{An Example}
Figure~\ref{fig:example1} show a function that is vulnerable to side-channel attacks. The function take a input secret from the caller. Depending on the value of the secret, it may access different values at line 7. Suppose an attacker can observe which item in the table \textsf{T} is accessed, he can infer the secret based on the observation.
\begin{figure}[h]
  \begin{minipage}{0.6\linewidth}
    \begin{lstlisting}[xleftmargin=.15\textwidth,xrightmargin=.30\textwidth]
void bar(uint8_t secret)
{
  uint8_t T[128];
  uint8_t index = 0, t;
  int i;
  index = (index+secret)%128;
  t = T[index];
  ...
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.4\linewidth}
    \resizebox{0.8\textwidth}{!}{%

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              & A &   &   &   &   &                 \\
        5              &   & A &   &   &   &   &             \\
        6              &   &   & A &   &   &   &             \\
        7              &   &   &   & A &   &   &   &         \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A minor leakage. }\label{chapter5:fig:example2}
\end{figure}
On the other hand, the second example also have a side-channel leakages at line 7. However, the leakage is slightly different. Still, we test the program with input from $0, 1, \dots, 7$. However, we find the attacker can not uniquely determine the secret based on the observation of table $T$. For example. both $0$ and $4$ read the first the item of the table. Therefore, we think the vulnerability is slightly minor than the previous one. Here comes with the definition of the amount of leaked information of the vulnerability.

@@

Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages. We can use the definition to detect those severe leakages. In the examples of Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys. In Figure~\ref{chapter5:fig:example1}, each item in the array could be read. Therefore, the channel capacity in Figure~\ref{chapter5:fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$. In Figure~\ref{chapter5:fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$. Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition is a conservative estimation.

@@

Considering the example in figure~\ref{fig:align}, it read the data from the array \textsf{T} based on the index (i). If the index (i) is associated with a key, it could be a side-channel vulnerability. Unlike the example in the previous section, the array \textsf{T} is on the heap. Data on the heap are allocated in different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run. For the example in Figure~\ref{fig:align}(a), the index that used to access the array is always $1$, so it should not be a side-channel vulnerability here. However, because the based address is different. So we get two different memory accesses. Under the circumstance, it is a false positive. Besides, it can cause false negatives as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different index. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ can not observe the difference here, which can cause a false positive.

@@

There are some possible solutions that can assign the value.
\textbf{Run-time Information.} One example here is the concrete memory address during the runtime. Such a value satisfy the uniqueness characteristic. However, as the example shown in Figure~\ref{fig:align}, it does not have the alignment property.
\textbf{Source Code Information.} Alternatively, we can use the information from the source code. Recent work~\cite{sumner2010memory} proposes using the execution point that allocate the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory. However, such a method may miss the alias symbol that points to the same memory cell.

We propose to combine both the information from the source code and the runtime to align the memory access during the execution. At the point the memory is allocated, we use the tuple $(start\ address, length)$ to represent the buffer. In the following execution, we check if any memory access falls into the range of those tuples. If so, we add the memory access into the tuple. After the execution, the tuple can be mapped into the location of the source code and we only compare the memory access that belongs to the same lines in the source code.

\section{Multiple Leakages Sites}
Real-world software can have many side-channel vulnerabilities. Those vulnerabilities may spread in the whole program. An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}. In order to precisely quantify the
total information leakage, we need to know the relation of those leakage sites.

@@

We use the chi-square test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $r*c$  two-way contingency table. The chi-square test statistic and the degrees of freedom $v$ is calculated with the below formula:
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\] 
\[v = (r - 1)(c - 1)\]
Here $O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.

>>>>

\subsection{An Example}
Figure~\ref{fig:example1} shows a function that is vulnerable to side-channel attacks. The function takes an input secret from the caller. Depending on the value of the secret, it may access different values at line 7. Suppose an attacker can observe which item in the table \textsf{T} is accessed. He can infer the secret based on the observation.

\begin{figure}[h]
  \begin{minipage}{0.6\linewidth}
    \begin{lstlisting}[xleftmargin=.15\textwidth,xrightmargin=.30\textwidth]
void bar(uint8_t secret)
{
  uint8_t T[128];
  uint8_t index = 0, t;
  int i;
  index = (index+secret)%128;
  t = T[index];
  ...
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.4\linewidth}
    \resizebox{0.8\textwidth}{!}{%

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              & A &   &   &   &   &                 \\
        5              &   & A &   &   &   &   &             \\
        6              &   &   & A &   &   &   &             \\
        7              &   &   &   & A &   &   &   &         \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A minor leakage. }\label{chapter5:fig:example2}
\end{figure}
On the other hand, the second example also has side-channel leakages at line 7. However, the leakage is slightly different. Still, we test the program with input from $0, 1, \dots, 7$. However, we find the attacker can not uniquely determine the secret based on the observation of table $T$, for example. Both $0$ and $4$ read the first item of the table. Therefore, we think the vulnerability is minor than the previous one. Here comes the definition of the amount of leaked information of the vulnerability.

@@

Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages. We can use the definition to detect those severe leakages. In the examples of Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, because the secret input range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys. In Figure~\ref{chapter5:fig:example1}, each item in the array could be read. Therefore, the channel capacity in Figure~\ref{chapter5:fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$. In Figure~\ref{chapter5:fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$. Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition~\ref{chapter5:def} is a conservative estimation.

@@

Considering the example in figure~\ref{fig:align}, it read the data from the array \textsf{T} based on the index (i). If index (i) is associated with a key, it could be a side-channel vulnerability. Unlike the example in the previous section, the array \textsf{T} is on the heap. Data on the heap are allocated in different addresses each time. Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run. For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here. However, because the based address is different. So we get two different memory accesses. Under the circumstance, it is a false positive. Besides, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b). In the example, different keys lead to different indexes. However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} can not observe the difference here, which can cause a false positive.

@@

There are some possible solutions that can assign the value.
\textbf{Run-time Information.} One example here is the concrete memory address during the runtime. Such a value satisfies the uniqueness characteristic. However, as the example shown in Figure~\ref{fig:align}, it does not have the alignment property.
\textbf{Source Code Information.} Alternatively, we can use the information from the source code. Recent work~\cite{sumner2010memory} proposes using the execution point that allocates the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory. However, such a method may miss the alias symbol that points to the same memory cell.

We propose to combine both the information from the source code and the runtime to align the memory access during the execution. At the point the memory is allocated, we use the tuple $(start\ address, length)$ to represent the buffer. In the following execution, we check if any memory access falls into the range of those tuples. If so, we add the memory access into the tuple. After the execution, the tuple can be mapped into the location of the source code, and we only compare the memory access that belongs to the same lines in the source code.

\section{Multiple Leakages Sites}
Real-world software can have many side-channel vulnerabilities. Those vulnerabilities may spread throughout the whole program. An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}. In order to precisely quantify the
total information leakage, we need to know the relation of those leakage sites.

@@

We use the chi-square test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $r*c$  two-way contingency table. The chi-square test statistic and the degrees of freedom $v$ are calculated with the below formula:
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad	 v = (r - 1)(c - 1)\]
Here $O$ is the observed value, and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
